The Gaia-ESO Survey: Combined estimates from multiple stellar analysis pipelines

### 2016-10-11 article/ms.tex
sum shit

We list the nomenclature and descriptions for all model parameters in Table 
\ref{tab:model-parameters}. The number of total model parameters is given by
\begin{eqnarray}
    N_{parameters} = N_{calibrators} + N_{missing} + 6N_{nodes} + \frac{N_{nodes}!}{2(N_{nodes} - 2)!}
\end{eqnarray}
where $N_{calibrators}$ accounts for the true values of the calibrators, the
$N_{missing}$ models the missing data points for the calibrator spectra, the
$6N_{nodes}$ summarises parameters that model biases, as well as systematic
and random uncertainties. The final term $\frac{N_{nodes}!}{2(N_{nodes} - 2)!}$
is the number of correlation coefficients between all nodes.\footnote{In practice
we include the Cholesky decomposition $L$ of the $N \times N$ correlation matrix $\rho$
as model parameters instead of directly modeling the $\rho$ terms.  The correlation
matrix can be reconstructed by $\rho = (IL)\cdot(IL)^T$ where $I$ is the $N \times N$
identity matrix. This parameterisation helps ensure that the resulting covariance
matrix $\mathbf{\Sigma}$ is positive semi-definite, and can therefore be used for
sampling.}

@@

% How does the model scale?

% The implementation details.
% Inheritly unstable
% Cholesky decomposition

>>>>

We list the nomenclature and descriptions for all model parameters in Table 
\ref{tab:model-parameters}. The number of total model parameters is given by
\begin{eqnarray}
    N_{parameters} = N_{calibrators} + N_{missing} + 6N_{nodes} + \frac{N_{nodes}!}{2(N_{nodes} - 2)!}
\end{eqnarray}
where $N_{calibrators}$ accounts for the true values of the calibrators, the
$N_{missing}$ models the missing data points for the calibrator spectra, the
$6N_{nodes}$ summarises parameters that model biases, as well as systematic
and random uncertainties. The final term $\frac{N_{nodes}!}{2(N_{nodes} - 2)!}$
is the number of correlation coefficients between all nodes.\footnote{
This inference problem is numerically unstable, as there are many model parameters
which are used toi

 construct a covariance matrix that is sampled

In practice
we include the Cholesky decomposition $L$ of the $N \times N$ correlation matrix $\rho$
as model parameters instead of directly modeling the $\rho$ terms.  The correlation
matrix can be reconstructed by $\rho = (IL)\cdot(IL)^T$ where $I$ is the $N \times N$
identity matrix. This parameterisation helps ensure that the resulting covariance
matrix $\mathbf{\Sigma}$ is positive semi-definite, and can therefore be used for
sampling.}

@@

We implemented the model in \texttt{Stan}, a probabilistic programming
language, and the code describing our parameterisation is included as Appendix \ref{
appendix:stan-code}. We initialised the model with $\mu_{true}$ at the central
calibrator values, and set XXXXXX, with no correlation between any nodes. We
optimized all parameters in \texttt{Stan} using the Broyden-Fletcher-Goldfarb-Shanno
algorithm. The optimized point was used as an initialisation point for Markov Chain
Monte-Carlo (MCMC) sampling.

N chains, thinning, N iterations. Convergence criteria.
